\chapter*{Abstract}
\label{cha:abstract}
Link prediction is the task of predicting the existence of a relation between two entities in a knowledge graph. To solve this task various research has been done to improve and create new models. Most of these models are from the sub-symbolic approach while not as much research has been done to create symbolic models. Recent published models like AnyBURL have shown that the symbolic models can compete with the more popular sub-symbolic models. 

In this master thesis the two approaches are compared in regard to their ability to correctly predict facts and focus on the characteristics of these facts. 

To be more precise, the prediction results of AnyBURL and three different sub-symbolic models were analysed to determine whether one of the approaches performs better if we only regard a subset of the test data which shares a common characteristic i.e. whether one of the approaches has an advantage if a triple has a certain characteristic. 

During this comparison it was found that the relation class and relation frequency of a triple has a slight influence on which approach performs better while the entity frequency did not show to have any influence. Moreover, it was found that the sub-symbolic approach performs better in predicting a triple if the trainings data already contained a similar triple while the symbolic approach achieved better results for triples without a similar triple. Lastly, clusters of similar entities were found where one of the approaches performed significantly better than the other. 